Docker as a Development Environment for Documenting Results

### 2020-11-25 ms.tex
fix README.md and change title

\title{Docker as a Development Environment for Research Papers}

@@

We propose a template for writing computational research papers with \LaTeX\ and verifying  its reproducibility using the concept of \textit{reproducible builds} (RBs) in a local or remote computational environment.
We provide an open source implementation of the template\footnote{\url{https://github.com/pbizopoulos/docker-as-a-development-environment-for-research-papers-template}}, which we use to write this paper\footnote{\url{https://arxiv.org/abs/2005.12660}} and verify its reproducibility\footnote{\url{https://github.com/pbizopoulos/docker-as-a-development-environment-for-research-papers}}.
We use Python~\cite{van2007python} for producing the results, however other scientific-oriented programming languages can be used.

@@

\bibliographystyle{IEEEtran}
\bibliography{ms}

>>>>

\title{Docker as a Development Environment for Documenting Results}

@@

We propose a template for writing computational research papers with \LaTeX\ and verifying  its reproducibility using the concept of \textit{reproducible builds} (RBs) in a local or remote computational environment.
We provide an open source implementation of the template\footnote{\url{https://github.com/pbizopoulos/docker-as-a-development-environment-for-documenting-results-template}}, which we use to write this paper\footnote{\url{https://arxiv.org/abs/2005.12660}} and verify its reproducibility\footnote{\url{https://github.com/pbizopoulos/docker-as-a-development-environment-for-documenting-results}}.
We use Python~\cite{van2007python} for producing the results, however other scientific-oriented programming languages can be used.

@@

\bibliographystyle{IEEEtran}
\bibliography{ms.bib}
